\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-23 thesis/abstract.tex
Corrected the abstract

\chapter*{Abstract}
For a long time humanity has fantasized that one day robots will walk among us.
They will move and be able to interact with us, understand our concepts and
be able to reason.
An important step on that direction is endowing robots with knowledge of human concepts and
semantics. However its unrealistic to believe on the possibility of extensively
describing human concepts and semantics to robots on a pre-deploy phase, and so, robots must be able
to adapt and learn when confronted with novel situations.
Detection of novel situations, where the robot knowledge is not sufficient, plays then an important
role for the subsequent adapting and learning of new concepts and its this thesis main topic.

In the context of mobile robotics, spatial concepts and semantics play a main role to perform
complex human-like tasks and human interactions. For handling those, a robot builds a representation
of space extended with semantic properties, process which is known as semantic mapping.
This representation identifies spatial entities and classifies them according to their meaning to
humans allowing the robot to reason at a very high-level.
For example, in a room scale, humans categorize space in kitchens, bedrooms, corridors,
office, theater, computer lab, etc\dots, by relating room areas with those categories, that describing expected
properties and actions that take place on them, a robot can solve tasks like:
``Where are the cornflakes?''

This thesis studies a proposed %~\cite{pronobis2011semmap}
process that utilizes spatial and semantic knowledge for semantic mapping using a
probabilistic graphical model,
and develops methods to perform detection of room categories not previously
known to the robot using that graphical model.
At last, it draws attention to the use of unlabelled data on the novelty detection process,
which can be used to considerably increase performance.

>>>>

\chapter*{Abstract}

For a long time humanity has dreamed that one day robots will be among us. They will explore our world
and interact with us, understand our concepts and reason. An important step in that direction is endowing 
robots with knowledge about human concepts and semantics. However, it is unrealistic to believe that the 
human world can be fully modeled in the robot's brain at the design stage. Therefore, robots must be able 
to adapt and learn when confronted with novel situations. Detection of novel situations, where the knowledge
of the robot is not sufficient plays an important role in adaptation and learning of new concepts and 
is the main topic of this thesis.

In the context of mobile robotics, spatial concepts and semantics are crucial to enable the robot to perform
complex human-like tasks and human interactions. For handling those, a robot builds a representation
of space extended with semantic properties, process which is known as semantic mapping.
This representation identifies spatial entities and classifies them according to their meaning to
humans allowing the robot to reason at a high abstraction level. For example, humans categorize spaces as 
kitchens, bedrooms, corridors, offices, theaters, computer labs, etc. based on spatial properties, 
objects and actions that are characteristic of those spaces. Similarly, if a robot had a knowledge about
those spatial concepts, it could answer such questions as: ``Where are cornflakes?''

This thesis studies a semantic mapping process that employs spatial semantic knowledge
and represents it using a probabilistic graphical model. It develops methods 
for performing detection of novel room categories which were not previously known to the robot applicable 
to that graphical model. Finally, it draws attention to the usefullness of unlabelled data for the 
novelty detection process in order to considerably increase the detection accuracy.
